Hydra Battles and Cie

### 2021-03-12 doc/part-hydras.tex
consistent use of capitalization in headers

\chapter{Hydras and Hydra Games}

@@

\section{A Long battle}
\label{sect:big-battle}

@@

\chapter{Introduction to Ordinal Numbers and Ordinal Notations}

@@

\chapter[A proof of termination, using epsilon0]{A Proof of Termination, using Ordinals below \texorpdfstring{$\epsilon_0$}{Epsilon0}}

@@

%---------------------------------------------------------------------
\chapter{Large Sets and Rapidly Growing Functions}\label{chap:alpha-large}

@@

%----------------------------------------------------------------------
\chapter[Countable Ordinals (after Sch\"{u}tte)]{Kurt Schütte's Axiomatic Definition of Countable Ordinals}

>>>>

\chapter{Hydras and hydra games}

@@

\section{A long battle}
\label{sect:big-battle}

@@

\chapter{Introduction to ordinal numbers and ordinal notations}

@@

\chapter[A proof of termination, using epsilon0]{A proof of termination, using ordinals below \texorpdfstring{$\epsilon_0$}{Epsilon0}}

@@

%---------------------------------------------------------------------
\chapter{Large sets and rapidly growing functions}\label{chap:alpha-large}

@@

%----------------------------------------------------------------------
\chapter[Countable ordinals (after Sch\"{u}tte)]{Kurt Schütte's axiomatic definition of countable ordinals}
